### 2012-03-27 doc/theses/mikula/experiments.tex
Master thesis: Corrections.

\begin{table}
\label{TAB_inferred_types}
\caption{Inferred type statements.}
\begin{tabular}{|l|}
\hline
\texttt{/site/open\_auctions/open\_auction/bidder/increase/text()} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/closed\_auctions/closed\_auction/price/text()} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/open\_auctions/open\_auction/initial/text()} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/open\_auctions/open\_auction/initial/text()} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/people/person/profile/@income} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/open\_auctions/open\_auction/reserve} $\rightarrow$ \texttt{decimal} \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}
\label{TAB_inferred_keys}
\caption{Inferred key statements.}
\begin{tabular}{|l|c|}
\hline
\textbf{Key} & \textbf{Weight} \\ \hline \hline
\texttt{(/site/closed\_auctions/closed\_auction, \{buyer/@person\})} & -1.0 \\ \hline
\texttt{(/site/regions/europe/item, \{@id\})} & -0.417 \\ \hline
\texttt{(/site/people/person, \{@id\})} & 1.0 \\ \hline
\texttt{(/site/closed\_auctions/closed\_auction, \{itemref/@item\})} & 0.417 \\ \hline
\end{tabular}
\end{table}

The first one is correct, a buyer is not a key of closed auctions. The second one is not correct, because \texttt{id} attribute is a key of \texttt{item} elements. The third one is correct and the forth one declares \texttt{itemref} element to be a key of closed auctions, which is not true, but only with weight 0.417.

@@

\begin{table}
\label{TAB_inferred_keys_2}
\caption{Key statements inferred from the extended test data.}
\begin{tabular}{|l|c|}
\hline
\textbf{Key} & \textbf{Weight} \\ \hline \hline
\texttt{(/site/closed\_auctions/closed\_auction, \{buyer/@person\})} & -1.0 \\ \hline
\texttt{(/site/regions/europe/item, \{@id\})} & -0.417 \\ \hline
\texttt{(/site/people/person, \{@id\})} & 1.0 \\ \hline
\texttt{(/site/closed\_auctions/closed\_auction, \{itemref/@item\})} & -0.417 \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}
\label{TAB_inferred_keys_3}
\caption{Key statements inferred from the extended test data using the modified JP3 statements.}
\begin{tabular}{|l|c|}
\hline
\textbf{Key} & \textbf{Weight} \\ \hline \hline
\texttt{(/site/people/person, \{@id\})} & 1.0 \\ \hline
\texttt{(/site/closed\_auctions/closed\_auction, \{itemref/@item\})} & -0.333 \\ \hline
\end{tabular}
\end{table}

\todo[inline]{Pripojit vysledne XSD? Je dost velke. Alebo aspon relevantnu cast?}

>>>>

\begin{table}
\begin{tabular}{|l|}
\hline
\texttt{/site/open\_auctions/open\_auction/bidder/increase/text()} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/closed\_auctions/closed\_auction/price/text()} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/open\_auctions/open\_auction/initial/text()} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/open\_auctions/open\_auction/initial/text()} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/people/person/profile/@income} $\rightarrow$ \texttt{integer} \\ \hline
\texttt{/site/open\_auctions/open\_auction/reserve} $\rightarrow$ \texttt{decimal} \\ \hline
\end{tabular}
\caption{Inferred type statements.}
\label{TAB_inferred_types}
\end{table}

@@

\begin{table}
\begin{tabular}{|l|c|}
\hline
\textbf{Key} & \textbf{Weight} \\ \hline \hline
\texttt{(/site/closed\_auctions/closed\_auction, \{buyer/@person\})} & -1.0 \\ \hline
\texttt{(/site/regions/europe/item, \{@id\})} & -0.417 \\ \hline
\texttt{(/site/people/person, \{@id\})} & 1.0 \\ \hline
\texttt{(/site/closed\_auctions/closed\_auction, \{itemref/@item\})} & 0.417 \\ \hline
\end{tabular}
\caption{Inferred key statements.}
\label{TAB_inferred_keys}
\end{table}

The first one is correct, a buyer is not a key of closed auctions. The second one is not correct, because \texttt{id} attribute is a key of \texttt{item} elements. The third one is correct and the fourth one declares \texttt{itemref} element to be a key of closed auctions, which is not true, but only with weight 0.417.

@@

\begin{table}
\begin{tabular}{|l|c|}
\hline
\textbf{Key} & \textbf{Weight} \\ \hline \hline
\texttt{(/site/closed\_auctions/closed\_auction, \{buyer/@person\})} & -1.0 \\ \hline
\texttt{(/site/regions/europe/item, \{@id\})} & -0.417 \\ \hline
\texttt{(/site/people/person, \{@id\})} & 1.0 \\ \hline
\texttt{(/site/closed\_auctions/closed\_auction, \{itemref/@item\})} & -0.417 \\ \hline
\end{tabular}
\caption{Key statements inferred from the extended test data.}
\label{TAB_inferred_keys_2}
\end{table}

@@

\begin{table}
\begin{tabular}{|l|c|}
\hline
\textbf{Key} & \textbf{Weight} \\ \hline \hline
\texttt{(/site/people/person, \{@id\})} & 1.0 \\ \hline
\texttt{(/site/closed\_auctions/closed\_auction, \{itemref/@item\})} & -0.333 \\ \hline
\end{tabular}
\caption[Key statements inferred using the modified JP3 statements.]{Key statements inferred from the extended test data using the modified JP3 statements.}
\label{TAB_inferred_keys_3}
\end{table}

\todo[inline]{Pripojit vysledne XSD? Je dost velke. Alebo aspon relevantnu cast? A: Neni treba, kdyz tak do appendixu.}
